Supporting Information

### 2018-02-13 All_analysis.Rmd
separate the plotter function and make the tester doc into the beginning of a sup mat

---
title: "Bivariate_analysis on different datasets"
author: "Shyamolina Ghosh"
date: "February 8, 2018"
output: 
  html_document:
    fig_caption: yes
    fig_width: 5
    highlight: zenburn
    keep_tex: yes
    number_sections: yes
    df_print: kable # data frame printing option
fontsize: 11pt
---
updated on `r Sys.Date()`
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<mark>*Code preloaded*</mark>

```{r BIVAN, echo=F}
library(copula)
source("OurBiCopSelect.R")

# This function takes a bivariable dataset (matrix or dataframe)
# Output : a plot(optional) and rankings as a dataframe

getcopula<-function(d,ploton){

  #get ranks
  v1<-d[,1]
  v2<-d[,2]

  #get ranks modified now
  if(max(rbind(v1,v2))>=1){
    v1<-pobs(v1)
    v2<-pobs(v2)
  }

  if(ploton==T){
    plot(v1,v2,type="p",col="red",xlab=expression(v[1]),ylab=expression(v[2]),cex.lab=1)
  }

  cop<-data.frame(v1=v1,v2=v2)
  return(cop)
}

#Test the function
#cop<-claytonCopula(8,2)
#d<-rCopula(1000,cop)
#cop_rank<-(getcopula(d=d,ploton=T))

#--------------------------------------------------------------------------------------------------
# This function fits the data within the given set of families
# Input : given data, a vector of possible copula families, indep_test_p threshold
# output : a list of two dataframe: 1. all possible info for bestfit cop, 
#                          2. info for all possible fit cop(copcode,copname,par,par1,logLik,AIC,BIC)

fit_BIV<-function(d,families,level=0.05){

  num_indep<-0

  m<-getcopula(d,ploton=F)
  u1<-m[,1]
  u2<-m[,2]

  ans<-OurBiCopSelect(u1,u2,families,AICBIC="AIC",level=0.05,numBS=100,gofnormal=T)
  if(ans$IndepTestRes<level){
    gfc_numBS<-100
    gfc_p_CvM<-ans$GofRes_CvM
    gfc_p_KS<-ans$GofRes_KS
    gfc_p_CvM_stat<-ans$GofRes_CvM_stat
    gfc_p_KS_stat<-ans$GofRes_KS_stat

    gfc_normal_p_CvM<-ans$GofRes_Normal_CvM
    gfc_normal_p_KS<-ans$GofRes_Normal_KS
    gfc_normal_p_CvM_stat<-ans$GofRes_Normal_CvM_stat
    gfc_normal_p_KS_stat<-ans$GofRes_Normal_KS_stat

    pmin<-min(ans$GofRes_CvM,ans$GofRes_KS,ans$GofRes_Normal_CvM,ans$GofRes_Normal_KS)
    if(pmin<0.2){
      ans2<-OurBiCopSelect(u1,u2,families,AICBIC="AIC",level=0.05,numBS=1000,gofnormal=T)
      gfc_numBS<-1000
      gfc_p_CvM<-ans2$GofRes_CvM
      gfc_p_KS<-ans2$GofRes_KS
      gfc_p_CvM_stat<-ans$GofRes_CvM_stat
      gfc_p_KS_stat<-ans$GofRes_KS_stat

      gfc_normal_p_CvM<-ans2$GofRes_Normal_CvM
      gfc_normal_p_KS<-ans2$GofRes_Normal_KS
      gfc_normal_p_CvM_stat<-ans$GofRes_Normal_CvM_stat
      gfc_normal_p_KS_stat<-ans$GofRes_Normal_KS_stat
    }

    info<-ans$InfCritRes
    info_ord<-info[order(info[,6],decreasing = F),] # ordered according to min to max AIC

  }else{
    num_indep<-num_indep+1
    gfc_numBS<-Inf
    gfc_p_CvM<-Inf
    gfc_p_KS<-Inf
    gfc_p_CvM_stat<-Inf
    gfc_p_KS_stat<-Inf
    gfc_normal_p_CvM<-Inf 
    gfc_normal_p_KS<-Inf
    gfc_normal_p_CvM_stat<-Inf
    gfc_normal_p_KS_stat<-Inf
    info_ord<-data.frame(copname="Indep")
  }

#-----------------------------------------------------------------------------
# Save the results
  RES<-list(data.frame(num_indep_location=num_indep,
               gfc_numBS=gfc_numBS,
               gfc_p_CvM=gfc_p_CvM,
               gfc_p_KS=gfc_p_KS,
               gfc_p_CvM_stat=gfc_p_CvM_stat,
               gfc_p_KS_stat=gfc_p_KS_stat,
               gfc_normal_p_CvM=gfc_normal_p_CvM,
               gfc_normal_p_KS=gfc_normal_p_KS,
               gfc_normal_p_CvM_stat=gfc_normal_p_CvM_stat,
               gfc_normal_p_KS_stat=gfc_normal_p_KS_stat),
               info_ord=info_ord)

  return(RES)

}

#-------------------------------------------------------------------------------------
#Check the function
#families<-c(1,3,5)
#x<-fit_BIV(d,families)
#---------------------------------------------------------------------------------------------------------

```

# Testing code

* **About the dataset :** This data came from a clayton with param=8

```{r loaddatatest, echo=F}
# here you can directly load the bivariate data to the variable d
# or you can save the bivariate data to d after some data extraction
d<-readRDS("Data/givendata.RDS")
```

* **Copula plot of the data :**
```{r callingcodetest, echo=F, cache=T, cache.extra=list(d)}
#Test the function
cop_rank<-(getcopula(d=d,ploton=T))

>>>>

---
title: "Exploring the importance of a complete statistical description of dependence in ecology and evolution"
author: "Shyamolina Ghosh and Daniel Reuman"
date: "February 8, 2018"
output: 
  html_document:
    fig_caption: yes
    fig_width: 5
    highlight: zenburn
    keep_tex: yes
    number_sections: yes
    df_print: kable # data frame printing option
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
seed<-101
families<-c(1,3:6,14)
source("getcopula.R")
source("OurBiCopSelect.R")
```

Updated on `r Sys.Date()`

# Template analysis

**About the dataset :** These data were simulated from a Clayton copula with parameter 8.

```{r load_data_test, echo=F}
#Load your data - should be a data frame with 2 columns. Can contain NAs.
d<-readRDS("Data/givendata.RDS")
```

**Copula plot of the data :**
```{r rankandplot_test, echo=F, cache=T, cache.extra=list(d)}
#convert to a copula and plot
v<-getcopula(d=d,rankon=F,ploton=T) #with real data, rankon should be T
```

**Bivariate copula model selection and goodness of fit pipeline:**
```{r bivmodselect_test, echo=F, cache=T, cache.extra=list(seed,d)}
x<-fit_BIV(d=d,families)
```

### 2018-02-13 SupportingInformation.Rmd
separate the plotter function and make the tester doc into the beginning of a sup mat

---
title: "For testing OurBiCopSelect.R"
author: "Daniel Reuman"
date: "February 12, 2018"
output: pdf_document
---

This is just for testing the `OurBiCopSelect.R` function. We test that
it runs and gives reasonable results by simulating data and seeing if 
you recover what kind of copula was used.

@@

>>>>

---
title: "Supporting Information"
author: "Shyamolina Ghosh and Daniel Reuman"
date: "February 12, 2018"
output: pdf_document
---

# Descriptions of data

# Testing the ranking and bivariate copula display function

This is just for testing the `getcopula` function.

<!--Source in function and a package--->
```{r}
source("getcopula.R")
require(copula)
require(mvtnorm)
```

Plot data from a Clayton copula, which has lower tail dependence:
```{r}
copC<-claytonCopula(8,2)
dC<-rCopula(1000,copC)
vC<-getcopula(d=dC,rankon=F,ploton=T)
```

Plot data from a Joe copula, which has upper tail dependence:
```{r}
copJ<-joeCopula(8,2)
dJ<-rCopula(1000,copJ)
vJ<-getcopula(d=dJ,rankon=F,ploton=T)
```

Get data from a bivariate normal distribution and take ranks and
then plot:
```{r}
sigma<-matrix(c(1,.7,.7,1),2,2)
dN<-rmvnorm(1000,mean=c(0,0),sigma=sigma)
vN<-getcopula(d=dN,rankon=T,ploton=T)
```

# Testing the bivariate model selection and goodness-of-fit pipeline

This is just for testing the `OurBiCopSelect` function. We test that
it runs and gives reasonable results by simulating data and seeing if 
you recover what kind of copula was used.

@@

# Testing the pipeline for examining tail dependence in bivariate data
